Comparing clustering parameters with rOpenScPCA

### 2025-01-14 analyses/hello-clusters/02_compare-clustering-parameters.Rmd
update a comment
addidentally deleted an r
ensure legend fits, and render the html

      # calculate neighbhorhood purity
      purity_df <- rOpenScPCA::calculate_purity(pca_matrix, silhouette_df)
    }
  )

@@

      # Plot the UMAP, colored by the new cluster variable
      ggplot(umap_df_plot, aes(x = UMAP1, y = UMAP2, color = cluster)) +
        geom_point(alpha = 0.6) +
        labs(title = umap_title) +
        # We'll add a couple UMAP-specific plot settings
        coord_equal() +
        theme(
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          legend.position = "bottom"
        )
    }
  )

>>>>

      # calculate neighbhorhood purity, starting from silhouette_df
      rOpenScPCA::calculate_purity(pca_matrix, silhouette_df)
    }
  )

@@

      # Plot the UMAP, colored by the new cluster variable
      ggplot(umap_df_plot, aes(x = UMAP1, y = UMAP2, color = cluster)) +
        geom_point(alpha = 0.6) +
        labs(title = umap_title) +
        # We'll add a couple UMAP-specific plot settings
        coord_equal() +
        theme(
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          # Ensure legends fit in the figure
          legend.position = "bottom",
          legend.key.size = unit(0.2, "cm")
        )
    }
  )
